---
title: "FSE_Survival"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(survival)
library(coxme)
library(car)
library(htmlTable)
#library(OIsurv)
library(sqldf)
#if (!require("devtools")) install.packages("devtools")
#devtools::install_github("mkuhn/dict")
#library("dict")
library(ggplot2)
library(survminer)
library(remotes)
library(pscl)
library(survMisc)

#install_version("cmprsk", "2.2-7")
```

## FSE Survival Analysis

This is a supplementary markdown file for FSE Submission title "Heard it through the GitVine: An Empirical Study of Tool Diffusion Across the npm Ecosystem."

## Defining Functions
```{r code block1, results='hide'}
get_df <- function(badge) {
  df <- read.csv(toString(badge), sep=",", stringsAsFactors = FALSE, header=FALSE)
  names(df) = c("repo_id","start_interval", "end_interval", "act_committers", "act_pullers", "act_watchers", "act_undir_committers",
                "tool_popularity", "all_popularity", "depsim", "depgraph", "desc", "n_commits", "n_committers", 
                "n_watchers", "n_org", "comp_badge", "other_badge", "adopted")
  
  df$adopted = as.factor(df$adopted)
  df$repo_id = as.factor(df$repo_id)
  df_stats = sqldf("select repo_id, count(*) as num_windows, max(adopted) as adopted from df group by repo_id")
  print(nrow(df_stats))
  
  
  summary(df_stats$num_windows)
  table(df_stats$num_windows)
  
  df_treatment = df_stats[df_stats$adopted == 1,]
  df_control = df_stats[df_stats$adopted == 0,][sample(nrow(df_stats),2*nrow(df_treatment)),]
  
  print(nrow(df_control))
  print(nrow(df_treatment))
  
  df.sample = rbind(df[df$repo_id %in% df_treatment$repo_id,],
                    df[df$repo_id %in% df_control$repo_id,])
  
  print("Sample Created")
  print(nrow(df.sample))
  print(table(df.sample$adopted))
  summary(df.sample[df.sample$adopted==1,]$start_interval)
  return(df.sample)
}
```

## Getting relevant data for badges.
```{r code block2, results='hide'}
df_travis <- get_df("travis")
df_circle <- get_df("circle")
df_appveyor <- get_df("appveyor")
df_codeship <- get_df("codeship")
df_david <- get_df("david")
df_bithound <- get_df("bithound")
df_gemnasium <- get_df("gemnasium")
df_coveralls <- get_df("coveralls")
df_codeclimate <- get_df("codeclimate")
df_codecov <- get_df("codecov")
df_codacy <- get_df("codacy")
df_saucelabs <- get_df("saucelabs")
df_slack <- get_df("slack")
df_gitter <- get_df("gitter")
df_license <- get_df("license")
df_npm_version <- get_df("npm-version")
df_npm_downloads <- get_df("npm-downloads")
```

## Running Survival Models -- David
```{r code block3, results='show'}
coxph_david <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_david)
summary(coxph_david)
#vif(coxph_david)
#anova(coxph_david)
```

## Running Survival Models -- Bithound
```{r code block_bithound, results='show'}
coxph_bithound <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       #+ log(depsim+1)
                       + log(desc+1)
                       , data=df_bithound)
summary(coxph_bithound)
#vif(coxph_bithound)
#anova(coxph_bithound)
```


## Running Survival Models -- Gemnasium
```{r code block_gemnasium, results='show'}
coxph_gemnasium <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       #+ (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_gemnasium)
summary(coxph_gemnasium)
#vif(coxph_gemnasium)
#anova(coxph_gemnasium)
```


## Running Survival Models -- Saucelabs
```{r code block_saucelabs, results='show'}
coxph_saucelabs <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_saucelabs)
summary(coxph_saucelabs)
#vif(coxph_saucelabs)
#anova(coxph_saucelabs)
```


## Running Survival Models -- slack
```{r code block_slack, results='show'}
coxph_slack <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       #+ (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_slack)
summary(coxph_slack)
#vif(coxph_slack)
#anova(coxph_slack)
```


## Running Survival Models -- gitter
```{r code block_gitter, results='show'}
coxph_gitter <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       #+ (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_gitter)
summary(coxph_gitter)
#vif(coxph_gitter)
#anova(coxph_gitter)
```


## Running Survival Models -- license
```{r code block_license, results='show'}
coxph_license <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       #+ (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_license)
summary(coxph_license)
vif(coxph_license)
anova(coxph_license)
```


## Running Survival Models -- npm-version
```{r code block_npmVersion, results='show'}
coxph_npm_version <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       #+ (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_npm_version)
summary(coxph_npm_version)
#vif(coxph_npm_version)
#anova(coxph_npm_version)
```


## Running Survival Models -- npm-downloads
```{r code block_npmDownloads, results='show'}
coxph_npm_downloads <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       #+ (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_npm_downloads)
summary(coxph_npm_downloads)
```


## Running Survival Models -- travis
```{r code block_travis, results='show'}
coxph_travis <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_travis)
summary(coxph_travis)
```


## Running Survival Models -- circle
```{r code block_circle, results='show'}
coxph_circle <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_circle)
summary(coxph_circle)
```


## Running Survival Models -- appveyor
```{r code block_appveyor, results='show'}
coxph_appveyor <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_appveyor)
summary(coxph_appveyor)
```

## Running Survival Models -- codeship
```{r code block_codeship, results='show'}
coxph_codeship <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       #+ log(depsim+1)
                       #+ log(desc+1)
                       , data=df_codeship)
summary(coxph_codeship)
```


## Running Survival Models -- coveralls
```{r code block_coveralls, results='show'}
coxph_coveralls <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_coveralls)
summary(coxph_coveralls)
```


## Running Survival Models -- codeclimate
```{r code block_codeclimate, results='show'}
coxph_codeclimate <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       #+ log(desc+1)
                       , data=df_codeclimate)
summary(coxph_codeclimate)
```


## Running Survival Models -- codecov
```{r code block_codecov, results='show'}
coxph_codecov <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       + (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_codecov)
summary(coxph_codecov)
```


## Running Survival Models -- codacy
```{r code block_codacy, results='show'}
coxph_codacy <- coxph(Surv(start_interval,
                            end_interval,
                            adopted == 1) ~
                       + log(n_commits+1)
                       + log(n_watchers+1)
                       + (other_badge > 0)
                       + log(all_popularity+1)
                       #+ (comp_badge>0)
                       + log(act_watchers+1)
                       + log(act_undir_committers+1)
                       + log(depgraph+1)
                       + log(depsim+1)
                       + log(desc+1)
                       , data=df_codacy)
summary(coxph_codacy)
vif(coxph_codacy)
anova(coxph_codacy)
```